---
title: "DVR_Project2" 
output: html_document
---

Our data was taken from <https://support.spatialkey.com/spatialkey-sample-csv-data/> The file we chose from this website is called TechCrunch Continental USA and contains the listing 1,460 company funding records reported by TechCrunch. 

##The Steps

###Step 1
The first step to produce our project was to look for the data. Our data was taken from <https://support.spatialkey.com/spatialkey-sample-csv-data/>. The file we chose from this website is called TechCrunch Continental USA and contains the listing 1,460 company funding records reported by TechCrunch. 

###Step 2
Once we chose our data we begun to set up the data to create the oracle database. We modified the R_ETL.R. file to load our csv file into our oracle account. This file can be found under the folder named 02 Data Wrangling by the name 'Set up.R'

Here's a summary of what our data looks like. You need to run the code in this file in order to proceed to get the data wrnaglings and visualization. 
```{r}
source("../01 Data/Summary_Data.R", echo = TRUE)
```

If like us you were wondering what the data in column 'round' stands for, here's an explanation: 
* Pre-funding: You build a prototype of your product.
* Seed Round: The funding necessary to launch your product.
* A Round: The funding necessary to get product traction.
* B Round: The funding necessary to scale your product

###Step 3
Once we had our data in place we continued by playing around with it. In the folder 02 Data Wrangling there's a script called First_RE.R where we began playing with our data using grep. 

```{r}
source("../02 Data Wrangling/First_RE.R", echo=TRUE)

```

###Step 4 
Here's our first data wrangling.Here we took our data, grouped it by state, counted the number of distinct companies (some companies did more than one fund raise) per state and displayed it in a view arranged in descending order.Some interesting things we found from our data was that the state with the most companies raising money were California with a total of 533 companies follower by New York with 83. There's a drastic difference between the two. 
```{r}
source("../02 Data Wrangling/DataWrangling1.R", echo=TRUE)

```


###Step 5
Here's our second data wrangling. In this one we used group_by(). 
```{r}
source("../02 Data Wrangling/DataWrangling2.R", echo=FALSE)
View(dw2)
```
```{r}
source("../03 Visualizations/DW2.R", echo=TRUE)

```

###Step 6 
Here's our third data wrangling. 
```{r}
source("../02 Data Wrangling/DataWrangling3.R", echo=TRUE)

```

